\documentclass[11pt]{article}
\usepackage{hyperref}

\title{My \LaTeX\ Document}
\author{Michelle Krummel}
\date{\today}

\begin{document}
%\!TEX root %decides which file build
\tableofcontents
\maketitle

\vspace{1cm}
This will produce \textit{italicized} text.

This will produce \textbf{bold face} text.

This will produce \textsc{small caps} text.

This will produce \texttt{typewriter font} text.

Please visit Michelle Krummel's website at \url{http://michellekrummel.com}.

Please visit Michelle Krummel's website at \href{http://michellekrummel.com}{My website}.

Please excuse my dear aunt Sally.\\
Paranthesis exponents multiplication division addition subtraction

\vspace{1cm}

Please excuse my dear aunt Sally.

Please excuse my \begin{large}dear aunt Sally\end{large}.

Please excuse my \begin{Large}dear aunt Sally\end{Large}.

Please excuse my \begin{huge}dear aunt Sally\end{huge}.

Please excuse my \begin{Huge}dear aunt Sally\end{Huge}.

Please excuse my \begin{normalsize}dear aunt Sally\end{normalsize}.

Please excuse my \begin{small}dear aunt Sally\end{small}.

Please excuse my \begin{scriptsize}dear aunt Sally\end{scriptsize}.

Please excuse my \begin{tiny}dear aunt Sally\end{tiny}.

\vspace{1cm}

\begin{center}
    This line is centered.
\end{center}

\begin{flushleft}
    This line is left-justified.
\end{flushleft}

\begin{flushright}
    This line is right-justified.
\end{flushright}

\tiny
This line is centered.

This line is left-justified.

This line is right-justified.

\pagebreak

\section{Linear Functions}
\subsection{Slope-Intercept Form}
\subsection{Example 1:}
\subsection{Example 2:}
\subsection{Standard Form}
\subsection{Point-Slope Form}
\section{Quadradic Functions}
\subsection{Vertex Form}
\subsection{Standard Form}
\subsection{Factored Form}
\end{document}